%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Original author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Modifications by:
% Eshwen Bhal <milanman.eshb@gmail.com>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[12pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\makeatletter
\patchcmd{\@sectioncolor}{\color}{\mdseries\color}{}{}
\makeatother

% Personal information (name, current position, contact details, websites/profiles)
\input{sections/personal_info}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}  % team
  {Company address}  % address
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for <such and such> role}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
 \makecvfooter
   {\today}
   {Eshwen Bhal~~~·~~~Cover Letter}
   {\thepage}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
Give a brief overview of my situation (recently completed PhD in particle physics, with a first class master’s degree in physics with astrophysics), personality, and goals in reference to the advertised job (e.g., that I'm excited to join and prove myself, etc.).

\lettersection{Why Google?}
Write a few sentences on why I am applying to the company, specifically.
What I like about them, and why they would be good to work for, etc. (could pull some things from the job spec. if it lists benefits).
    
\lettersection{Why Me?}
The most important bit.
Show how the experience and skills I've obtained so far (from PhD, teaching, undergrad) are suitable for the job and make me a good candidate.
These can include specific technical skills (programming in various languages and with various Python libraries, distributed computing, physics research, cutting edge particle physics) and more general, but useful skills (communication from scientific writing and conference speaking, collaboration from working in several small and large groups of multinational researchers).
Try to give specific examples of things, e.g., quickly learning ins and outs of detector for trigger/on call shifts, applying all my knowledge and skillsets in my PhD to achieve world leading results for Higgs boson to invisible state branching ratio, giving several large/conference level talks on behalf of the people in my group (i.e., not necessarily work I'd done, so requires lots of liaising with people and disseminating their contributions that I'm not an expert in).
Include keywords from job spec. where possible.
    
\end{cvletter}
    
%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing
    
\end{document}