\cvsection{Experience}

\begin{cventries}

        \cventry
        {Data Scientist} % Job title
        {Huboo Technologies} % Organization
        {Bristol, United Kingdom} % Location
        {Apr. 2022 -- Present} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{Member of the Innovation team at a fulfilment startup, providing novel, \textbf{data-driven solutions} to business problems.}
                \item{Overhauled internal and client analytics reporting to self-service \textbf{API-driven} platform. Greatly freed up developer resources.}
                \item{Developing \textbf{ML forecasting} API for automated replenishment of stock. Experimentation in \textbf{PyTorch} and \textbf{TensorFlow}, logged with \textbf{MLflow}. Deployment with Kubernetes on AWS.}
                \item{Optimised \textbf{SQL} queries for MySQL databases and Snowflake data warehouse, for data analysis and ETL.}
                \item{Built \textbf{CI pipelines} for automated code linting, formatting, testing, and documentation creation in \textbf{monorepo}.}
            \end{cvitems}
        }

    \cventry
        {Data Scientist} % Job title
        {Office for National Statistics} % Organization
        {Newport, United Kingdom} % Location
        {Feb. 2021 -- Apr. 2022} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{\textbf{Web scraped} prices of products from various retailers to vastly improve accuracy of Consumer Price Index.}
                \item{Built spiders with \textbf{Scrapy} in Python to reliably scrape thousands of products from dozens of websites.}
                \item{Introduced vital coding practices like \textbf{unit testing}, vectorisation, and automated documentation.}
                \item{Deployed spiders on \textbf{Google Cloud Platform}. Incorporated Docker, Terraform, and Kubernetes for optimal resourcing.}
            \end{cvitems}
        }

%    \cventry
%        {Computational Physics Tutor} % Job title
%        {University of Bristol} % Organization
%        {Bristol, United Kingdom} % Location
%        {2019 -- 2020} % Date(s)
%        {
%            \begin{cvitems} % Description(s) of tasks/responsibilities
%                \item{Taught Python to third year undergraduate students, with applications for \textbf{numerically solving physics problems} with NumPy and visualisation with matplotlib. Emphasis on \textbf{vectorisation} over looping, clear code, and presentation of results. Formally marked assignments in \textbf{Jupyter Notebooks} and provided feedback.}
%            \end{cvitems}
%        }

%    \cventry
%        {Mathematics Tutor} % Job title
%        {University of Bristol} % Organization
%        {Bristol, United Kingdom} % Location
%        {2017} % Date(s)
%        {
%            \begin{cvitems} % Description(s) of tasks/responsibilities
%                \item{Taught mathematics for physicists to first year undergraduate students. Formally marked problem sheets, orchestrated discussions with the students, and taught concepts for subsequent assignments.}
%            \end{cvitems}
%        }

\end{cventries}
