\cvsection{Experience}

\begin{cventries}

    \cventry
        {Data Scientist} % Job title
        {Office for National Statistics} % Organization
        {Newport, United Kingdom} % Location
        {2021 -- Present} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{\textbf{Web scraping} products and prices from various retailers to create a more accurate Consumer Price Index.}
                \item{Building spiders with Scrapy in Python to reliably scrape websites. Data cleaning and validation with \textbf{NumPy} and \textbf{pandas}.}
                \item{Introduced vital coding practices like \textbf{unit testing}, efficiency, and automated documentation.}
                \item{Assisting with maintenance and deployment of spiders on \textbf{Google Cloud Platform} for scheduled, automated execution. Incorporating Docker, Terraform, and Kubernetes for optimal deployment.}
            \end{cvitems}
        }

    \cventry
        {Computational Physics Tutor} % Job title
        {University of Bristol} % Organization
        {Bristol, United Kingdom} % Location
        {2019 -- 2020} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{Taught Python to third year undergraduate students, with applications for \textbf{numerically solving physics problems} with NumPy and visualisation with matplotlib. Emphasis on \textbf{vectorisation} over looping, clear code, and presentation of results. Formally marked assignments in \textbf{Jupyter Notebooks} and provided feedback.}
            \end{cvitems}
        }

%    \cventry
%        {Mathematics Tutor} % Job title
%        {University of Bristol} % Organization
%        {Bristol, United Kingdom} % Location
%        {2017} % Date(s)
%        {
%            \begin{cvitems} % Description(s) of tasks/responsibilities
%                \item{Taught mathematics for physicists to first year undergraduate students. Formally marked problem sheets, orchestrated discussions with the students, and taught concepts for subsequent assignments.}
%            \end{cvitems}
%        }

\end{cventries}
