\cvsection{Skills}

\newcommand{\vpaddingskills}{\vspace{1mm}}

\begin{cventries}
    \cventry
    {} % Empty position
    {Software and computing expertise} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Developed analysis software for dark matter searches and detector-effect calibrations in Python and C++. Optimised to run complex set of modules over billions of events on timescale of 1 hour.}
        \item {High proficiency in Python and use of data processing libraries like numpy and pandas. Using fully-vectorised approach often to reduce inefficiency.}
        \item {Visualisation with matplotlib and ROOT. Diverse range of graphs, charts, tables, and figures used to showcase results. Formal presentations of results with LaTeX and Microsoft PowerPoint.}
        \item {Utilisation of high performance computing and parallel programming with HTCondor and various computing grids.}
        \item{Expertise in git, bash, command line interface on Unix systems (Scientific Linux, CentOS, macOS).}
        \item {Meticulously and clearly documented code and running instructions for users.}
        \vpaddingskills
        \end{cvitems}
    }

    \cventry
    {}
    {Collaboration}
    {}
    {}
    {
      \begin{cvitems}
        \item {Belonging to, and working alongside, several groups of around a dozen people as well as a global research collaboration of over 4,000 people.}
        \vpaddingskills
        \end{cvitems}
    }

    \cventry
    {}
    {Problem solving}
    {}
    {}
    {
      \begin{cvitems}
        \item {Principal component of any physics degree. As an undergraduate, conducted more traditional pen-and-paper problem solving in many topics. As a PhD student, wrote code to solve physics problems numerically and perform data analysis for high energy particle physics.}
        \vpaddingskills
        \end{cvitems}
    }

    \cventry
    {}
    {Communication}
    {}
    {}
    {
      \begin{cvitems}
        \item {Presented formally in my PhD at all levels: regular working group updates, research group and collaboration-wide talks, and several conference posters and talks.}
        \item {Participated in outreach to the public at the CERN Open Days 2019 and at @Bristol.}
        \end{cvitems}
    }

\end{cventries}
