\cvsection{Skills}

\begin{cventries}

    \cventry
    {} % Empty position
    {Data analysis} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Primary focus of my PhD concerned statistical analysis of multi-terabyte datasets collected by the CMS experiment from the LHC.}
        \item {Developed analysis software for dark matter searches and detector-effect calibrations in Python and C++, using modern data science tools and batch processing for optimal efficiency. Ability to analyse \textbf{billions of events} on timescale of 1 hour.}
        \item {Visualisation with ROOT, matplotlib, and plotly. Formal presentations of results with LaTeX, PowerPoint, and Jupyter Notebooks.}
        \end{cvitems}
    }

    \cventry
    {} % Empty position
    {Software and computing expertise} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {\textbf{High proficiency in Python} and use of data processing libraries, \textbf{NumPy and pandas}. Allows vectorised performant approach.}
        \item {Utilisation of \textbf{high performance computing} and parallel programming with HTCondor and various computing grids.}
        \item {Adept in cloud technologies like Google Cloud Platform, AWS, Docker, Terraform, Kubernetes.}
        \item {Additional expertise in LaTeX, git, bash, command line interface on Unix systems (Scientific Linux, CentOS, macOS).}
        \end{cvitems}
    }

    \cventry
    {}
    {Collaboration}
    {}
    {}
    {
      \begin{cvitems}
        \item {Belonged to, and worked alongside, several groups of around a dozen people as well as a \textbf{global research collaboration} of over 4,000 people.}
        \end{cvitems}
    }

    \cventry
    {}
    {Problem solving}
    {}
    {}
    {
      \begin{cvitems}
        \item {Principal component of any physics degree. As an undergraduate, conducted traditional pen-and-paper problem solving in many topics. As a PhD student, wrote code to \textbf{solve physics problems numerically} and analyse high energy particle physics data.}
        \item {In industry, solving complex business problems led by data. Created versatile and scalable web scraping pipeline to capture thousands of products each day. Introduced comprehensive unit testing to identify bugs.}
        \end{cvitems}
    }

    \cventry
    {}
    {Communication}
    {}
    {}
    {
      \begin{cvitems}
        \item {Presented formally in my PhD at all levels: regular working group updates, research group and collaboration-wide talks, and several \textbf{conference posters and talks}.}
        \item {Participated in \textbf{public outreach} at the CERN Open Days 2019 and @Bristol. \textbf{Taught computing} and maths to undergraduates.}
        \end{cvitems}
    }

\end{cventries}
