\cvsection{Skills}

  % ADD AT LEAST SOME OF THE FOLLOWING:
  % LEADERSHIP (ORGANISING AND HELPING OUT JUNIOR PHD STUDENTS AND DELEGATING ASPECTS OF ANALYSIS)
  % OTHER STUFF: ON-CALL EXPERT FOR A CMS DETECTOR SUBSYSTEM (CALO LAYER-2) WHILE BASED AT CERN. UNDERTAKEN SHIFTS TO MONITOR AND MAINTAIN ONE OF THE PRINCIPAL SYSTEMS (LEVEL-1 TRIGGER) DURING DATA TAKING WHILE BASED AT CERN.
  % Could potentially list the above with \cvskill command, giving the skill as the first argument and a brief description as the second. Or I can try just listing everything in bullet points (similar to \cventry command but without the extra stuff. Or maybe they can be laid out like the Projects section in https://github.com/eshwen/my-cv/blob/74d372eecd96525d0c85c50d93380084f1d83a93/cv.pdf (code to typeset it: https://github.com/eshwen/my-cv/blob/74d372eecd96525d0c85c50d93380084f1d83a93/sections/projects.tex)

\newcommand{\vpadding}{\vspace{0.5mm}}

\begin{cventries}

    \cventry
    {} % Empty position
    {Data analysis} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {The primary focus of my PhD concerns statistical analysis of large (multi-terabyte) datasets collected by the CMS experiment from the Large Hadron Collider.}
        \item {Developed analysis software in Python and C++, using modern data science tools and distributed computing.}
        \item{Visualisation with ROOT and matplotlib. Formal presentations of results with LaTeX and Microsoft PowerPoint.}
        \vpadding
        \end{cvitems}
    }

    \cventry
    {} % Empty position
    {Collaboration} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Belonging to several working groups of around a dozen people as well as a wider collaboration of over 4,000 people.}
        \vpadding
        \end{cvitems}
    }

    \cventry
    {} % Empty position
    {Problem solving} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Predominant component of a physics degree. As an undergraduate, conducted more traditional pen-and-paper problem solving in many topics. As a PhD student, wrote code to solve physics problems numerically and perform data analysis.}
        \vpadding
        \end{cvitems}
    }

    \cventry
    {} % Empty position
    {Multitasking} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Often working on multiple projects at once with different working groups during PhD.}
        \vpadding
        \end{cvitems}
    }

    \cventry
    {} % Empty position
    {Organisation} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Coordinating different aspects of analyses in my PhD, meticulously documenting programming instructions and procedures of analysis components.}
        \vpadding
        \end{cvitems}
        }

    \cventry
    {} % Empty position
    {Communication} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Presented formally in my PhD at all levels: regular working group updates, research group and collaboration-wide talks, and several conference posters and talks.}
        \item {Participated in outreach to the public at the CERN Open Days 2019 and at @Bristol.}
        \end{cvitems}
    }

\end{cventries}

% Consider adding publications somewhere as well. Can update when SVJ and Hinv papers are published.
% Consider booking appointment with Careers Service when CV is done so they can check it (see http://www.bristol.ac.uk/careers/cv-application/). Also send around to other people (parents, other colleagues, Henning and Joel?)
